### 2023-07-25 tex/lr.tex
[ writing ] full draft

  Addition represents an intersection of guarantees.
  For example, if a variable is used covariantly in one subterm and
  contravariantly in another, we can only make the trivial guaratee represented
  by $\gr{\sim\sim}$.
  Multiplication is mainly interesting for multiplication by
  $\gr{\downarrow\downarrow}$, which flips the variance on any other annotation.
  As such, $\oc\gr{\downarrow\downarrow}A$ represents a contravariant $A$.
  The flipping (involutive) behaviour of $\gr{\downarrow\downarrow}$ lets us
  notice that $x$ is covariant in
  a term like $-(-x)$, where $-$ is a constant of type
  $\oc\gr{\downarrow\downarrow}\mathbb Z \multimap \mathbb Z$.

>>>>

  Addition represents an intersection of guarantees.
  For example, if a variable is used covariantly in one subterm and
  contravariantly in another, we can only make the trivial guarantee represented
  by $\gr{\sim\sim}$.
  Multiplication is mainly interesting for multiplication by
  $\gr{\downarrow\downarrow}$, which flips the variance on any other annotation.
  As such, $\oc\gr{\downarrow\downarrow}A$ represents a contravariant $A$.
  The flipping (involutive) behaviour of $\gr{\downarrow\downarrow}$ lets us
  notice that $x$ is covariant in
  a term like $-(-x)$, where $-$ is a constant of type
  $\oc\gr{\downarrow\downarrow}\mathbb Z \multimap \mathbb Z$.

### 2023-07-25 tex/modal.tex
[ writing ] full draft

\begin{proposition}\label{thm:NKT4-P}
  In NJ + \TirName{N} + \TirName{K} + \TirName{4}, the following principle is
  admissible.
  \[
    \ebrule{%
      \hypo{\Box B_1, \ldots, \Box B_n \vdash A}
      \infer1[Promotion]{\Box B_1, \ldots, \Box B_n \vdash \Box A}
    }
  \]
\end{proposition}
\begin{proof}
  By induction on $n$.
  When $n = 0$, \TirName{Promotion} becomes just the necessitation rule \TirName{N}.
  For $n = \lvert\Gamma\rvert + 1$, we have the following derivation, where
  $\Box\Gamma$ abbrevates
  $\Box\Gamma_1, \ldots, \Box\Gamma_{\lvert\Gamma\rvert}$ and \TirName{4$'$} and
  \TirName{K$'$} abbrevate the obvious combinations of
  \TirName{4} and \TirName{K}, respectively, and \TirName{$\to$-E}.
  I silently apply weakening thoughout the derivation for the sake of concision.
  \[
    \begin{prooftree}
      \hypo{\Box\Gamma, \Box B \vdash A}
      \infer1[$\to$-I]{\Box\Gamma \vdash \Box B \to A}
      \infer1[IH]{\Box\Gamma \vdash \Box\plr{\Box B \to A}}
      \infer0[Var]{\Box B \vdash \Box B}
      \infer1[4$'$]{\Box B \vdash \Box\Box B}
      \infer2[K$'$]{\Box\Gamma, \Box B \vdash \Box A}
    \end{prooftree}
  \]
\end{proof}

\begin{proposition}\label{thm:PT-NKT4}
  In NJ + \TirName{Promotion} + \TirName{T}, we can derive the original axioms
  and rule of S4: \TirName{N}, \TirName{K}, \TirName{T}, and \TirName{4}
\end{proposition}
\begin{proof}
  The rule \TirName{N} and axiom \TirName{T} are immediate.
  For axioms \TirName{K} and \TirName{4}, we have the following derivations,
  where \TirName{T$'$} abbrevates the obvious combination of \TirName{T} and
  \TirName{$\to$-E}.
  \begin{mathpar}
    \ebrule{%
      \infer0[T$'$]{\Box\plr{A \to B} \vdash A \to B}
      \infer0[T$'$]{\Box A \vdash A}
      \infer2[$\to$-E]{\Box\plr{A \to B}, \Box A \vdash B}
      \infer1[Promotion]{\Box\plr{A \to B}, \Box A \vdash \Box B}
      \infer1[$\to$-I]{\Box\plr{A \to B} \vdash \Box A \to \Box B}
      \infer1[$\to$-I]{\vdash \Box\plr{A \to B} \to \Box A \to \Box B}
    }
    \and
    \ebrule{%
      \infer0[Var]{\Box A \vdash \Box A}
      \infer1[Promotion]{\Box A \vdash \Box\Box A}
      \infer1[$\to$-I]{\vdash \Box A \to \Box\Box A}
    }
  \end{mathpar}
\end{proof}

>>>>

\begin{proposition}\label{thm:NKT4-P}
  In NJ + \TirName{N} + \TirName{K} + \TirName{4}, the following principle is
  admissible.
  \[
    \ebrule{%
      \hypo{\Box B_1, \ldots, \Box B_n \vdash A}
      \infer1[Promotion]{\Box B_1, \ldots, \Box B_n \vdash \Box A}
    }
  \]
\end{proposition}
\begin{proof}
  By induction on $n$.
  When $n = 0$, \TirName{Promotion} becomes just the necessitation rule \TirName{N}.
  For $n = \lvert\Gamma\rvert + 1$, we have the following derivation, where
  $\Box\Gamma$ abbreviates
  $\Box\Gamma_1, \ldots, \Box\Gamma_{\lvert\Gamma\rvert}$ and \TirName{4$'$} and
  \TirName{K$'$} abbreviate the obvious combinations of
  \TirName{4} and \TirName{K}, respectively, and \TirName{$\to$-E}.
  I silently apply weakening throughout the derivation for the sake of concision.
  \[
    \begin{prooftree}
      \hypo{\Box\Gamma, \Box B \vdash A}
      \infer1[$\to$-I]{\Box\Gamma \vdash \Box B \to A}
      \infer1[IH]{\Box\Gamma \vdash \Box\plr{\Box B \to A}}
      \infer0[Var]{\Box B \vdash \Box B}
      \infer1[4$'$]{\Box B \vdash \Box\Box B}
      \infer2[K$'$]{\Box\Gamma, \Box B \vdash \Box A}
    \end{prooftree}
  \]
\end{proof}

\begin{proposition}\label{thm:PT-NKT4}
  In NJ + \TirName{Promotion} + \TirName{T}, we can derive the original axioms
  and rule of S4: \TirName{N}, \TirName{K}, \TirName{T}, and \TirName{4}
\end{proposition}
\begin{proof}
  The rule \TirName{N} and axiom \TirName{T} are immediate.
  For axioms \TirName{K} and \TirName{4}, we have the following derivations,
  where \TirName{T$'$} abbreviates the obvious combination of \TirName{T} and
  \TirName{$\to$-E}.
  \begin{mathpar}
    \ebrule{%
      \infer0[T$'$]{\Box\plr{A \to B} \vdash A \to B}
      \infer0[T$'$]{\Box A \vdash A}
      \infer2[$\to$-E]{\Box\plr{A \to B}, \Box A \vdash B}
      \infer1[Promotion]{\Box\plr{A \to B}, \Box A \vdash \Box B}
      \infer1[$\to$-I]{\Box\plr{A \to B} \vdash \Box A \to \Box B}
      \infer1[$\to$-I]{\vdash \Box\plr{A \to B} \to \Box A \to \Box B}
    }
    \and
    \ebrule{%
      \infer0[Var]{\Box A \vdash \Box A}
      \infer1[Promotion]{\Box A \vdash \Box\Box A}
      \infer1[$\to$-I]{\vdash \Box A \to \Box\Box A}
    }
  \end{mathpar}
\end{proof}

### 2023-07-25 tex/rec.tex
[ writing ] full draft

The bunched connectives give us a means by which to quickly design and
experiment with new type systems.
We will see in \cref{sec:framework} that all such syntaxes are well behaved to
the extend that they all support the appropriate notion of substitution, which
again expediates experimentation.
In this section, I give some example syntactic features that can be covered in
the bunched connective paradigm.

@@

I presented $\name$ as an essentially arbitrary collection of rules, with no
broader characterisation than that it intuitively seems to capture some notion
of ``usage'' and that it supports the semantics I give in \cref{sec:wrel}.
Therefore, in this subsection I give some examples of variant syntaxes others,
with different use cases, may be interested in.
In particular, I give a variant of function types where usage annotations go
``on the arrow'', and a variant of tensor products with a stronger elimination
rule.

@@

Following \cref{sec:lnd}, I want to turn the ad hoc constraints on $\grP$,
$\grQ$, and $\grR$ into the result of some premise combinators.
To do this, I introduce a new combinator $\Box^{0{+}}$ defined below,
along with the resulting implicit-context typing rules.

>>>>

The bunched connectives give us a means by which to quickly design and
experiment with new type systems.
We will see in \cref{sec:framework} that all such syntaxes are well behaved to
the extend that they all support the appropriate notion of substitution, which
again expedites experimentation.
In this section, I give some example syntactic features that can be covered in
the bunched connective paradigm.

@@

I presented $\name$ as an essentially arbitrary collection of rules, with no
broader characterisation than that it intuitively seems to capture some notion
of ``usage'' and that it supports the semantics I give in \cref{sec:den-sem}.
Therefore, in this subsection I give some examples of variant syntaxes others,
with different use cases, may be interested in.
In particular, I give a variant of function types where usage annotations go
``on the arrow'', and a variant of tensor products with a stronger elimination
rule.

@@

Following \cref{sec:lnd}, I want to turn the ad hoc constraints on $\grP$,
$\grQ$, and $\grR$ into the result of some premise connectives.
To do this, I introduce a new connective $\Box^{0{+}}$ defined below,
along with the resulting implicit-context typing rules.

### 2023-07-25 tex/semantics.tex
[ writing ] full draft

In this chapter, the central construct is a function \AgdaFunction{semantics}
which, for a $\V$-environment $\rho : \Gamma \env\V \Delta$,
maps a term $M : \Delta \vdash A$ to some semantic value in the type
$\C\,\Gamma\,A$.
This is a direct adaptation of the \AgdaFunction{semantics} function of
\cref{sec:gen-sem}, which has the same kind of action on intuitionistic terms,
given similar operations on $\V$ and $\C$ as what we had earlier.
The \AgdaFunction{semantics} function recurses on the term $M$, updating $\rho$
whenever new variables are bound.
In our usage-aware case, $\rho$ is also updated whenever we come across linear
combinations induced by premise combinators $I^{\sep}$, $\sep$, and
$\gr r \cdot {}$.

This chapter is structured as follows.
I start by giving a quick introduction to linear relations --- a generalisation
of linear maps --- with reference to their use in mechanised algebraic
reasoning, in \cref{sec:lin-rel}.
Using linear relations, I give a functorial \emph{map} operation to a single
layer of syntax in \cref{sec:functorial}.
I then adapt the \AgdaFunction{Kripke} function space to the usage-aware
setting in \cref{sec:kripke}.
Then I apply the \AgdaFunction{Kripke} function space, along with much of the
machinery I have introduced in previous chapters, to give the
\AgdaFunction{semantics} function in \cref{sec:traversal}.
Finally, I give the syntax-generic simultaneous renaming and substitution
operations in \cref{sec:kit-to-sem}.

@@

\AgdaFunction{Wrap}
is a device that turns any type family into an equivalent type family
that is judgementally injective in its indices, which helps with
Agda's type inference.
It turns the type family into a parametrised
record with a single field \AgdaField{get} whose type is the type in
the body of the $\lambda$-abstraction.
For understanding the meaning of
\AgdaFunction{Kripke}, \AgdaFunction{Wrap} can be ignored.

@@

\begin{lemma}[\AgdaFunction{reify}]\label{thm:reify}
  If $\V$ is an open family such that there is a function
  $v : {\sqni} \rightarrowtriangle \V$, we get a function of type
  $\mathrm{Kripke}\,\V\,\C \rightarrowtriangle \mathrm{Scope}\,\C$ for any $\C$.
\end{lemma}
\begin{proof}
  Let $b : \mathrm{Kripke}\,\V\,\C\,\Delta\,\Gamma\,A$.
  That is, $b$ is a Kripke function yielding $\C$-computations
  We want to apply $b$ so as to get a $\C\,\plr{\Gamma, \Delta}\,A$.
  Let $\grP\gamma = \Gamma$ and $\grQ\delta = \Delta$.
  The $\Box^r$ in the type of $b$ allows us to reverse-rename $\Gamma$ to
  $\Gamma, \gr0\delta$.
  Then we give the $\wand$-function an argument in context
  $\gr0\gamma, \Delta$, noting that
  $\plr{\Gamma, \gr0\delta} + \plr{\gr0\gamma, \Delta} = \plr{\Gamma, \Delta}$,
  as we wanted from the result.
  The argument needs type $\gr0\gamma, \Delta \env\V \Delta$.
  We produce this via \cref{thm:env-postren} from an environment
  $\rho : \gr0\gamma, \Delta \env\V \gr0\gamma, \Delta$ created using $v$
  and a renaming which is the complement to that used on $\Box^r$.
\end{proof}

@@

>>>>

In this chapter, the central construct is a function \AgdaFunction{semantics}
which, for a $\V$-environment $\rho : \Gamma \env\V \Delta$,
maps a term $M : \Delta \vdash A$ to some semantic value in the type
$\C\,\Gamma\,A$.
This is a direct adaptation of the \AgdaFunction{semantics} function of
\cref{sec:gen-sem}, which has the same kind of action on intuitionistic terms,
given similar operations on $\V$ and $\C$ as what we had earlier.
The \AgdaFunction{semantics} function recurses on the term $M$, updating $\rho$
whenever new variables are bound.
In our usage-aware case, $\rho$ is also updated whenever we come across linear
combinations induced by premise connectives $I^{\sep}$, $\sep$, and
$\gr r \cdot {}$.

This chapter is structured as follows.
I start by giving a quick introduction to linear relations --- a generalisation
of linear maps --- with reference to their use in mechanised algebraic
reasoning, in \cref{sec:lin-rel}.
Using linear relations, I give a functorial \emph{map} operation to a single
layer of syntax in \cref{sec:functorial}.
I then adapt the \AgdaFunction{Kripke} function space to the usage-aware
setting in \cref{sec:kripke}.
Then I apply the \AgdaFunction{Kripke} function space, along with much of the
machinery I have introduced in previous chapters, to give the
\AgdaFunction{semantics} function in \cref{sec:traversal}.
Finally, I show that the Kripke function space simplifies under certain
conditions in \cref{sec:reify}, and I use that case to give the syntax-generic
simultaneous renaming and substitution operations in \cref{sec:kit-to-sem}.

@@

\AgdaFunction{Wrap}
is a device that turns any type family into an equivalent type family
that is definitionally injective in its indices, which helps with
Agda's type inference.
It turns the type family into a parametrised
record with a single field \AgdaField{get} whose type is the type in
the body of the $\lambda$-abstraction.
For understanding the meaning of
\AgdaFunction{Kripke}, \AgdaFunction{Wrap} can be ignored.

@@

\begin{lemma}[\AgdaFunction{reify}]\label{thm:reify}
  If $\V$ is an open family such that there is a function
  $v : {\sqni} \rightarrowtriangle \V$, we get a function of type
  $\mathrm{Kripke}\,\V\,\C \rightarrowtriangle \mathrm{Scope}\,\C$ for any $\C$.
\end{lemma}
\begin{proof}
  Let $b : \mathrm{Kripke}\,\V\,\C\,\Delta\,\Gamma\,A$.
  That is, $b$ is a Kripke function yielding $\C$-computations
  We want to apply $b$ so as to get a $\C\,\plr{\Gamma, \Delta}\,A$.
  Let $\grP\gamma = \Gamma$ and $\grQ\delta = \Delta$.
  The $\Box^r$ in the type of $b$ allows us to reverse-rename $\Gamma$ to
  $\Gamma, \gr0\delta$.
  Then we give the $\wand$-function an argument in context
  $\gr0\gamma, \Delta$, noting that
  $\plr{\Gamma, \gr0\delta} + \plr{\gr0\gamma, \Delta} = \plr{\Gamma, \Delta}$,
  as we wanted from the result.
  The argument needs type $\gr0\gamma, \Delta \env\V \Delta$.
  We produce this via \cref{thm:ren-env-comp} from an environment
  $\rho : \gr0\gamma, \Delta \env\V \gr0\gamma, \Delta$ created using $v$
  and a renaming which is the complement to that used on $\Box^r$.
\end{proof}

@@

\section{Conclusion}

In this chapter, I have completed my generalisation of the core of the work of
\citet{AACMM21}.
The key decision to be made in this generalisation process was that the Kripke
function spaces would be based on the $\wand$ bunched connective.
That this change works justifies the idea of a deep connection between linear
syntaxes and bunched-logic-style handling of contexts.

The main pay-off we have seen so far from this and the previous chapter is that
all syntaxes we can describe respect substitution.
However, in the following chapter, I give more specific worked examples using
the generic semantic traversal and operations derived from it.

### 2023-07-25 tex/syntax.tex
[ writing ] full draft

The \AgdaDatatype{Premise} data type describes premises of rules,
using the bunched combinators from \cref{fig:bunched}. A single
premise is introduced by the
\AgdaInductiveConstructor{$\langle$\_`$\vdash$\_$\rangle$}
constructor.  This allows binding of additional variables
\AgdaBound{$\Delta$} (with specified types and usage annotations) and
the specification of a conclusion type \AgdaBound{A} for this premise.
The remaining constructors are descriptions for the
bunched connectives. %, and will be interpreted directly as such, below.

@@

Terms in this data type are difficult to write by hand, due to the
need for proofs that the usage contexts are handled correctly. For
example, the following term is needed to show that, in the $\{\gr0,
\gr1, \gr\omega\}$ (linearity) posemiring of \cref{def:lin-semiring},
$\oc\gr\omega$ forms a comonad.
Pattern synonyms \AgdaInductiveConstructor{$\multimap$I},
\AgdaInductiveConstructor{!E$'$}, and
\AgdaInductiveConstructor{!I$'$} stand for applications of
\AgdaInductiveConstructor{`con}, with the latter two taking explicit usage
contexts and proofs.
On concrete
posemirings (as in this example), unification is particularly poor at
inferring the usage contexts from the proofs because addition and
multiplication are no longer (judgementally) injective.
The function \AgdaFunction{var\#} is a way of turning a statically known de
Bruijn level and a usage proof into an application of \AgdaInductiveConstructor{`var}.

@@

The \AgdaFunction{uvar\#} tool is like the \AgdaFunction{var\#} tool I used
earlier --- allowing us to refer to variables by counting from the lefthand end
of the context.
I add these numbers to the picture of the graph for convenience.
Variables never go out of scope, despite being used, so these numbers do not
change with any bindings.

@@

Finally, while there is a simple and well motivated core of premise combinators
--- $\dot1$, $\dottimes$, $I^{\sep}$, $\sep$, and $\gr r \cdot \plr{-}$ --- the
various $\Box$-modalities feel like ad hoc additions.
While I have shown that $\Boxzp$ and $\Boxzpt$ have several practical uses, it
is unclear whether there should be more modalities.
Furthermore, I have not made an effort to isolate the properties that make these
modalities well behaved.
We will see in \cref{sec:functorial} that any such modality will need to be
functorial in the appropriate sense, but other examples of generic programming,
such as the usage elaborator which will be detailed in
\cref{sec:usage-elaborator}, may need further properties.

>>>>

The \AgdaDatatype{Premise} data type describes premises of rules,
using the bunched connectives from \cref{fig:bunched}. A single
premise is introduced by the
\AgdaInductiveConstructor{$\langle$\_`$\vdash$\_$\rangle$}
constructor.  This allows binding of additional variables
\AgdaBound{$\Delta$} (with specified types and usage annotations) and
the specification of a conclusion type \AgdaBound{A} for this premise.
The remaining constructors are descriptions for the
bunched connectives. %, and will be interpreted directly as such, below.

@@

Terms in this data type are difficult to write by hand, due to the
need for proofs that the usage contexts are handled correctly. For
example, the following term is needed to show that, in the $\{\gr0,
\gr1, \gr\omega\}$ (linearity) posemiring of \cref{def:lin-semiring},
$\oc\gr\omega$ forms a comonad.
Pattern synonyms \AgdaInductiveConstructor{$\multimap$I},
\AgdaInductiveConstructor{!E$'$}, and
\AgdaInductiveConstructor{!I$'$} stand for applications of
\AgdaInductiveConstructor{`con}, with the latter two taking explicit usage
contexts and proofs.
On concrete
posemirings (as in this example), unification is particularly poor at
inferring the usage contexts from the proofs because addition and
multiplication are no longer (definitionally) injective.
The function \AgdaFunction{var\#} is a way of turning a statically known de
Bruijn level and a usage proof into an application of \AgdaInductiveConstructor{`var}.

@@

The \AgdaFunction{uvar\#} tool is like the \AgdaFunction{var\#} tool I used
earlier --- allowing us to refer to variables by counting from the left-hand end
of the context.
I add these numbers to the picture of the graph for convenience.
Variables never go out of scope, despite being used, so these numbers do not
change with any bindings.

@@

Finally, while there is a simple and well motivated core of premise connectives
--- $\dot1$, $\dottimes$, $I^{\sep}$, $\sep$, and $\gr r \cdot \plr{-}$ --- the
various $\Box$-modalities feel like ad hoc additions.
While I have shown that $\Boxzp$ and $\Boxzpt$ have several practical uses, it
is unclear whether there should be more modalities.
Furthermore, I have not made an effort to isolate the properties that make these
modalities well behaved.
We will see in \cref{sec:functorial} that any such modality will need to be
functorial in the appropriate sense, but other examples of generic programming,
such as the usage elaborator which will be detailed in
\cref{sec:usage-elaborator}, may need further properties.

### 2023-07-25 tex/terms.tex
[ writing ] full draft

We could mechanise Gentzen's definition of a natural deduction system directly,
but this definition is quite complicated.
In particular, if we want to give derivations an inductive definition, the use
of the discharge mechanism means that we actually need an inductive-inductive
type --- derivations, particularly those using $\to$-introduction, can involve
references to assumptions within their subderivations.
An inductive-inductive definition of derivations would complicate our programs
and proofs about natural deduction derivations, so I choose an alternative
representation.

>>>>

As part of the Curry-Howard correspondence, terms of a $\lambda$-calculus
correspond to derivations in a natural deduction system.
We could mechanise Gentzen's original definition of a natural deduction system
directly, but this definition is quite complicated.
In particular, if we want to give derivations an inductive definition, the use
of the discharge mechanism means that we actually need an inductive-inductive
type --- derivations, particularly those using $\to$-introduction, can involve
references to assumptions within their subderivations.
An inductive-inductive definition of derivations would complicate our programs
and proofs about natural deduction derivations, so I choose an alternative
representation.

### 2023-07-25 tex/trans.tex
[ writing ] full draft

The types of DILL are the same as the types of \name, except for the
restriction of $\oc\gr{r}$ to just $\oc\gr\omega$.
I will write the latter simply as $\oc$ when it appears in DILL\@.
I add sums and with-products to the calculus of \cite{Barber1996}, with the
obvious rules (stated fully in \cref{fig:dill2}).
These additive type formers present no additional difficulty to the translation.

@@

\subsection{Pfenning Davies}\label{sec:trans-pd}

The translation to and from the modal system of Pfenning and Davies
\cite{judgmental} (henceforth \emph{PD}) is similar to the translation to and
from DILL\@.
I present my variant of PD, again adding some common connectives, in
\cref{fig:pd}
The main difference is the algebra at which \name{} is instantiated.

@@

>>>>

The types of DILL are the same as the types of \name, except for the
restriction of $\oc\gr{r}$ to just $\oc\gr\omega$.
I will write the latter simply as $\oc$ when it appears in DILL\@.
I add sums and with-products to the calculus of \citet{Barber1996}, with the
obvious rules (stated fully in \cref{fig:dill2}).
These additive type formers present no additional difficulty to the translation.

@@

\subsection{Pfenning-Davies}\label{sec:trans-pd}

The translation to and from the modal system of \citet{judgmental}
(henceforth \emph{PD}) is similar to the translation to and from DILL\@.
I present my variant of PD, again adding some common connectives, in
\cref{fig:pd}
The main difference is the algebra at which \name{} is instantiated.

@@

Additionally, PD has no direct equivalents to the tensor unit and tensor
products.
Therefore, I note that if the semiring of usage annotations satisfies some
simple but strong criteria (as $\instPD$ does), then we can use the Cartesian
unit and products in their stead.

\begin{lemma}\label{thm:top-meet}
  If $\gr1 \leq \gr0$ and $\gr1 \leq \gr1 + \gr1$, then $I$ is interderivable
  with $\top$, and for all $A$ and $B$, $A \otimes B$ is interderivable with
  $A \with B$.
\end{lemma}
\begin{proof}
  The following derivations suffice.
  I omit standard inequalities to emphasise those which use this lemma's
  assumptions.
  \begin{mathpar}
    \ebrule{%
      \infer0[$\top$-I]{\gr1I \vdash \top}
    }
    \and
    \ebrule{%
      \infer0{\plr{\gr1} \leq \plr{\gr0}}
      \infer1[$I$-I]{\gr1\top \vdash I}
    }
    \and
    \ebrule{%
      %\infer0{\plr{\gr1} \leq \plr{\gr1 + \gr0}}
      \infer0[Var]{\gr1\plr{A \otimes B} \vdash A \otimes B}
      \infer0{\plr{\gr0, \gr1, \gr1} \leq \plr{\gr0, \gr1, \gr0}}
      \infer1[Var]{\gr0\plr{A \otimes B}, \gr1A, \gr1B \vdash A}
      \infer0{\plr{\gr0, \gr1, \gr1} \leq \plr{\gr0, \gr0, \gr1}}
      \infer1[Var]{\gr0\plr{A \otimes B}, \gr1A, \gr1B \vdash B}
      \infer2[$\with$-I]{\gr0\plr{A \otimes B}, \gr1A, \gr1B \vdash A \with B}
      \infer2[$\otimes$-E]{\gr1\plr{A \otimes B} \vdash A \with B}
    }
    \and
    \ebrule{%
      \infer0{\plr{\gr1} \leq \plr{\gr1} + \plr{\gr1}}
      \infer0[Var]{\gr1\plr{A \with B} \vdash A \with B}
      \infer1[$\with$-E$_0$]{\gr1\plr{A \with B} \vdash A}
      \infer0[Var]{\gr1\plr{A \with B} \vdash A \with B}
      \infer1[$\with$-E$_1$]{\gr1\plr{A \with B} \vdash B}
      \infer3[$\otimes$-I]{\gr1\plr{A \with B} \vdash A \otimes B}
    }
  \end{mathpar}
\end{proof}

\begin{remark}
  By multiplying through on both sides, $\gr1 \leq \gr0$ is equivalent to
  $\forall\gr x.~\gr x \leq \gr0$, and $\gr1 \leq \gr1 + \gr1$ is equivalent to
  $\forall\gr x.~\gr x \leq \gr x + \gr x$.
\end{remark}

Finally, I give the translation itself.
